%\documentclass[sigconf]{acmart}
%\documentclass[sigconf,10pt,anonymous]{acmart}
\documentclass[sigconf,10pt]{acmart}

\usepackage{balance} % For balanced columns on the last page
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{subcaption}
\usepackage{xspace}

% Copyright
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference info
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\settopmatter{printacmref=true, printccs=true, printfolios=false} %folios not allowed for Mobi 20'

%\copyrightyear{2020}
%\acmYear{2020}
%\setcopyright{acmcopyright}
\acmConference[CE7490]{Distributed Systems}{Semester 1}{Nanyang Technological University, Singapore}

\begin{document}
\title{RAID-6 atop S3}

\author{Ismail Lotfi and Amalinda Gamage}

 \affiliation{
    \department {School of Computer Science and Engineering}
   \institution{Nanyang Technological University}
   \city{Singpore}
 }
 \email{{ismail003,jath0001}@e.ntu.edu.sg}

\begin{abstract}
Inexpensive, reliable storage is increasingly required for both businesses and the homes.
As disk capacities increase and multiple drives are combined in one system, the probability of multiple disk failures increases.
An idea originally refereed as \textit{Redundant Array of Inexpensive Disks}  (RAID) and now refereed as \textit{Redundant Array of Independent Disks} RAID proposes a range of RAID versions to solve this problem.
This work focuses on RAID-6.
RAID-6 is an improvement to the functionality of RAID-5 by an additional block of parity and tolerates up to two arbitrary concurrent disk failures.
The key contribution of our work is the implementation and evaluation of a basic RAID-6 system atop multiple geo-distributed S3 storage buckets.
We briefly state below several additional advanced features this RAID-6 implementation offers.
First our implementation incorporates an unlimited files of arbitrary names and sizes.
The unlimited nature in the number of files is the result of exploiting S3 object storage buckets as the main storage medium.
Second, it supports a range of user intended RAID-6 disk configurations such as numbers of data, parity disks and file chuck sizes.
Lastly, it also handles automatic detection of S3 object based storage disk failures as well their recovery.
Our implementation is available at: \url{https://github.com/Amalinda/RAID6}.
\end{abstract}

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10003033.10003058.10003065</concept_id>
       <concept_desc>Networks~Wireless access points, base stations and infrastructure</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[500]{Storage~Redundancy, S3 and RAID-6}

\keywords{Geo-distributed Reliable Storage}

\maketitle

\input{introduction.tex}
\input{primer.tex}
\input{systemImplementation.tex}
\input{evaluation.tex}
\input{lessons.tex}

\section*{Acknowledgments}
The authors would like to thank Prof. Datta for the provided opportunity which aided in exploring a number of technologies related to distributed storage systems.

\balance
\bibliographystyle{ACM-Reference-Format}
\bibliography{reference}

\end{document}